\renewcommand{\keywords}{{\itshape \bfseries Keywords - }}
\chapter*{Abstract} 

Artificial intelligence is no longer just a futuristic promise, but a reality that is redefining the way we interact with the world and conduct business. From healthcare to the manufacturing industry, AI has demonstrated its ability to radically transform diverse fields, unleashing a series of changes that are revolutionising today. Artificial intelligence will enable the automation of a wide range of complex processes that currently still require human intervention.  

\vspace{5mm}

Artificial intelligence which, through methods, techniques and algorithms, provides computers the ability of identifying patterns in massive data and make predictions (predictive analytics). This learning allows computers to carry out specific tasks autonomously, i.e. without the need to be programmed.

\vspace{5mm}

The constant innovation and evolution of the emerging technologies, paired with the use by the vast majority of the world’s population, has led to organisations exploiting the power of the automatic learning methods to help them extract better quality information, increase productivity, reduce the costs and get more value form their data.

\vspace{5mm}

In an ever-evolving world where technology is redefining the way we live, agriculture is no exception. Artificial intelligence is emerging as a key tool to help farmers adapt to the effects of climate change and lessen its impact. By capitalising on artificial intelligence, farmers can make informed, data-driven decisions and anticipate the climate shifts.

\vspace{5mm}

This research deals with sustainable production systems in the cultivation of fig trees and the study of water needs in order to design irrigation strategies using a set of automatic learning techniques belonging to the world of artificial intelligence.

\vspace{5mm}

Lastly, once the results generated by the entire system created have been obtained, these will be analysed and the solutions to the problems presented will be identified. These will allow us to observe the degree of efficiency of the experiments developed and to know if they meet the proposed targets.


\keywords{Artificial Intelligence, Agriculture, Climate change}
